Fail Faster

### 2025-03-21 paper/paper.tex
update figs

We chart a path forward.
First, we show how to use \textit{multi-stage programming}, a classic technique for 
building fast DSLs “without regret”~\cn{}, to eliminate the overhead of 
many common generator abstractions. We refer to this approach as \name.
Second, we demonstrate that the source of entropy is an underappreciated design factor by 
isolating its runtime cost and showing that significant speedups can be achieved 
while preserving output equivalence.
These insights lay the groundwork for generator libraries that combine high-level 
design with low-level performance.

@@

\begin{figure}[h]
  % \includegraphics[scale=0.33]{allocs.png}
  \includegraphics[scale=0.45]{time.png}
  \caption{Time to generate using each strategy. Performance benefits scale with generation size (lower lines translate to greater performance benefit). BQ is \bq; Staged SR is \camlname using \bq's \texttt{splittable\_random} RNG; Staged CSR is \camlname using \secref{subsection:faster-rng}'s \csplitmix.}
  \label{fig:time}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.4]{scala.png}
 \caption{
  \jwc{Don't explain the chart in the caption, split this into two different charts --- purple on one, green on the other.}
  \jwc{Also can we use the language's colors for this?}
  \scalaname has better performance relative to ScalaCheck than \camlname relative to \bq. SC is ScalaCheck; BQ is \bq. Comparison is for a fixed size of 100.}
 \label{fig:scala}
 \end{figure}

>>>>

We chart a path forward.
First, we show how to use \textit{multi-stage programming}, a classic technique for 
building fast DSLs “without regret”~\cn{}, to eliminate the overhead of 
many common generator abstractions. We refer to this approach as \name.
Second, we demonstrate that a generator's source of entropy is an underappreciated design factor by 
isolating its runtime cost and showing that significant speedups can be achieved 
while preserving output equivalence.
These insights lay the groundwork for generator libraries that combine high-level 
design with low-level performance.

@@

\begin{figure}[h]
  % \includegraphics[scale=0.33]{allocs.png}
  \includegraphics[scale=0.32]{time.png}
  \caption{Time to generate using each strategy. Performance benefits scale with generation size (lower lines translate to greater performance benefit). BQ is \bq; Staged SR is \camlname using \bq's \texttt{splittable\_random} RNG; Staged CSR is \camlname using \secref{subsection:faster-rng}'s \csplitmix.}
  \label{fig:time}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.46]{scala.png}
 \caption{
  \jwc{Don't explain the chart in the caption, split this into two different charts --- purple on one, green on the other.}
  \jwc{Also can we use the language's colors for this?}
  \scalaname has better performance relative to ScalaCheck than \camlname relative to \bq. SC is ScalaCheck; BQ is \bq. Comparison is for a fixed size of 100.}
 \label{fig:scala}
 \end{figure}
